Greenhouse gas emissions model

### 2021-11-10 GHG_model_report.Rmd
Update some inputs, update graph,...

```{r graph-mermaid-manure, echo=FALSE, fig.width=10, fig.height=1}
mermaid("
        graph LR
        C(Central collection)-->B(Burned); linkStyle 0 stroke: red, stroke-width:1px
                                B-->P(Pasture); linkStyle 1 stroke: red, stroke-width:1px
        C-->D(Daily spread); linkStyle 2 stroke: green, stroke-width:1px
            D-->S(Sold); linkStyle 3 stroke: red, stroke-width:1px
                S-->L(Liquid storage); linkStyle 4 stroke: red, stroke-width:1px
                    L-->Co(Composted); linkStyle 5 stroke: red, stroke-width:1px
                        Co-->Dl(Dry lot); linkStyle 6 stroke: red, stroke-width:1px
                             Dl-->St(Solid storage); linkStyle 7 stroke: red, stroke-width:1px
                    L-->Bi(Biogas); linkStyle 8 stroke: green, stroke-width:1px
                        Bi-->Ls(Liquid slurry); linkStyle 9 stroke: red, stroke-width:1px
        ")
```

>>>>

```{r graph-mermaid-manure, echo=FALSE, fig.width=4, fig.height=1}
mermaid("
        graph LR
        C(Central collection)-->B(Burned); linkStyle 0 stroke: red, stroke-width:1px
                                B-->P(Pasture); linkStyle 1 stroke: red, stroke-width:1px
        C-->D(Daily spread); linkStyle 2 stroke: green, stroke-width:1px
            D-->S(Sold); linkStyle 3 stroke: red, stroke-width:1px
                S-->L(Liquid storage); linkStyle 4 stroke: red, stroke-width:1px
                    L-->Co(Composted); linkStyle 5 stroke: red, stroke-width:1px
                        Co-->Dl(Dry lot); linkStyle 6 stroke: red, stroke-width:1px
                             Dl-->St(Solid storage); linkStyle 7 stroke: red, stroke-width:1px
                    L-->Bi(Biogas); linkStyle 8 stroke: green, stroke-width:1px
                        Bi-->Ls(Liquid slurry); linkStyle 9 stroke: red, stroke-width:1px
        ")
```
